\LARGE \bf A Teachable Robotic Agent for Children Learning Handwriting, Capable of Simulated Handwriting Itself

### 2014-11-27 main.tex
R2 make clearer that shape models weren't our contribution

We believe that this article introduces three noteworthy contributions: an innovative
application of data processing and artificial intelligence for the generation and
learning of hand-written letters suitable for educative purposes; a robotic
system which has been experimentally proven to provide convincing scaffolding for
complex human-robot interactions (teacher-learner social interactions, learning by
demonstration, simulated robotic fine motor skills); and an initial experimental investigation of what appears to be a
new role for robots in education.

@@

    \item developing a system for generating poorly written letters appropriate
        for simulating a na\"ive learner in the context of handwriting, achieved
        by using statistical shape models through PCA of observations of the
        trajectory of the same letter;% * <deanna.m.hood@gmail.com> 2014-10-03T00:52:47.503Z:
%
% this is pretty "done before" so might want to play it down
%

    \item developing an algorithm capable of incorporating user feedback and
        demonstrations in order to adapt the generated handwriting quality so as
        to simulate a teachable agent, which has been implemented by maintaining
        a learning algorithm in the parameter space of the shape models and
        converging towards the parameters of user demonstrations; and

>>>>

We believe that this article introduces three noteworthy contributions: an innovative
application of data processing and artificial intelligence for the
learning of hand-written letters suitable for educative purposes; a robotic
system which has been experimentally proven to provide convincing scaffolding for
complex human-robot interactions (teacher-learner social interactions, learning by
demonstration, simulated robotic fine motor skills); and an initial experimental investigation of what appears to be a
new role for robots in education.

@@

    \item developing an algorithm capable of incorporating user feedback and
        demonstrations in order to adapt artificially generated handwriting quality so as
        to simulate a teachable agent, which has been implemented by maintaining
        a learning algorithm in the parameter space of the PCA-based shape models and
        converging towards the parameters of user demonstrations; and
